Tomographic galaxy clustering with the Subaru Hyper Suprime-Cam first year public data release

### 2019-10-02 doc/Paper/main.tex
typo

In terms of physics we show that a simple flux magnitude cut can be used to create useful samples for galaxy clustering analysis. This contrasts with other approaches that focus on red central galaxies to create smaller samples with more reliable redshift (see e.g. \cite{1507.05460,1807.10163}). Using magnitude cuts yield more galaxies that decrease the shot noise and thus improve the total statistical sensitivity of the survey despite somewhat lower bias leading to less pronounced clustering. In particular, the halo model results in observed galaxies occupying smaller halos toward higher redhifts, but these trends can be well understood by looking at how faint red galaxies drop out from our selection. These results confirm the phenomenological observation that galaxy bias scales approximately inversely with growth function, leading to redshift independent clustering at large redshifts. Our measured evolution of bias is thus consistent with previous measurements, such as those from DEEP2 survey \cite{Coil:2004} and also the LSST forecasting exercises, which assumed $b(z) = 0.95/D(z)$ \cite{1809.01669}. \as{should we comment on number density compared to SRD?}

>>>>

In terms of physics we show that a simple flux magnitude cut can be used to create useful samples for galaxy clustering analysis. This contrasts with other approaches that focus on red central galaxies to create smaller samples with more reliable redshift (see e.g. \cite{1507.05460,1807.10163}). Using magnitude cuts yield more galaxies that decrease the shot noise and thus improve the total statistical sensitivity of the survey despite somewhat lower bias leading to less pronounced clustering. In particular, the halo model results in observed galaxies occupying smaller halos toward higher redhifts, but these trends can be well understood by looking at how faint red galaxies drop out from our selection. These results confirm the phenomenological observation that galaxy bias scales approximately inversely with growth function, leading to redshift independent clustering at large redshifts. Our measured evolution of bias is thus consistent with previous measurements, such as those from DEEP2 survey \cite{Coil:2004} and are also in agreement the LSST forecasting exercises, which assumed $b(z) = 0.95/D(z)$ \cite{1809.01669} to better than 5\%. \as{should we comment on number density compared to SRD?}
